The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-07-01 borel-regularity.tex
Tidy up Borel whole derivatives statement

$\borel_\zeta\big[z^\lambda\, \series{\Phi}\big]=\fracderiv{\lambda}{\zeta}{0}\,\borel_\zeta\series{\Phi}$ for every $\lambda\in(-\infty, 0)$;
\item\label{res:whole-deriv-borel} \textbf{Whole derivatives} let $k\in\Z_{\ge 0}$ and $\series{\Phi}\in z^{-k-1}\llbracket z^{-1}\rrbracket_1$, then $\borel_\zeta\big[\partial_z^{k} \series{\Phi}\big]=(-\zeta)^k\borel_\zeta\series{\Phi}$.\footnote{This property holds more generally for series in $\C\llbracket z^{-1}\rrbracket$, even ones that are not $1$-Gevrey.}
\end{enumerate} 
\end{prop}
\begin{proof} 
Result~\ref{res:frac-deriv-borel} follows from Lemma~\ref{lem:frac-deriv-Borel}.

>>>>

$\borel_\zeta\big[z^\lambda\, \series{\Phi}\big]=\fracderiv{\lambda}{\zeta}{0}\,\borel_\zeta\series{\Phi}$ for every $\lambda\in(-\infty, 0)$;
\item\label{res:whole-deriv-borel} \textbf{Whole derivatives}

$\borel_\zeta\big[\partial_z^{k} \series{\Phi}\big]=(-\zeta)^k\borel_\zeta\series{\Phi}$ for all $k\in\{0, 1, 2, 3, \ldots\}$, under the condition that $\series{\Phi}\in z^{-k-1}\llbracket z^{-1}\rrbracket_1$.\footnote{This property holds for all series in $\C\llbracket z^{-1}\rrbracket$, even ones that are not $1$-Gevrey.}
\end{enumerate} 
\end{prop}
\begin{proof} 
Result~\ref{res:frac-deriv-borel} follows from Lemma~\ref{lem:frac-deriv-Borel}.
